Choosing climate forcing for numerical simulations of the Cordilleran ice sheet

### 2013-02-18 sections/model.tex
Added missing references

We use PISM, a parallel ice sheet model (version stable 0.5.11). Documentation on the code can be found in several publications \citep[e.g.,][]{bueler-brown-2009,aschwanden-etal-2012} and more extensively online \citep[{\url{http://www.pism-docs.org}},][]{web:pism}.

>>>>

We use PISM, a parallel ice sheet model (version stable 0.5.11). Documentation on the code can be found in several publications \citep[e.g.,][]{bueler-brown-2009,winkelmann-etal-2011,aschwanden-etal-2012} and more extensively online \citep[{\url{http://www.pism-docs.org}},][]{web:pism}.
